Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
Updates

\subsection{CI Tests and Measures of Conditional Association}
Our DAG structure learning approach relies on using CI tests and a measure of
conditional association between variables -- also known as partial association
-- between variables. Specifically, firstly we are interested in testing a CI
test: $ X \ci Y \bm{Z} $, i.e., whether the variables $ X $ and $ Y $ are
independent when conditioned on $ \bm{Z} $. Secondly, we are interested in
quantifying the strength of relationship between $ X $ and $ Y $ conditioned on
$ \bm{Z} $. We can quantify this using the effect size measures of the CI
tests. In this section, we give an overview of some of the commonly used CI
tests for various data types and their effect size measures.

@@

\subsection{Model Testing Using CI Tests}

>>>>

\subsection{CI Tests and Measures of Conditional Association}
Our structure learning approach relies on using CI tests and a measure of
conditional association between variables -- also known as partial association.
Specifically, we are interested in testing CI tests: $ X \ci Y \bm{Z} $, i.e.,
whether the variables $ X $ and $ Y $ are independent when conditioned on $
\bm{Z} $. Secondly, we are interested in quantifying the strength of
relationship between $ X $ and $ Y $ conditioned on $ \bm{Z} $. We can use
the effect size measures of the CI tests for this quantification. In this 
section, we give an overview of some of the commonly used CI tests for 
various data types and their effect size measures.

@@

\subsection{Model Testing Using CI Tests}
Our structure learning algorithm relies on suggesting modifications to the
expert based on CI testing. In this section, we show an example of how this
works. Our structure learning algorithm can be thought of an iterative
application of this model testing approach.
